A GPU Sonar Simulator for Automatic Target Recognition

### 2014-04-30 UAM2014/Article/article.tex
la2pdf commit - 2014:04:30	14:15:28	(Wed30.Apr)

\subsection{OpenGL Rendering}

@@

If we place the camera at the sonar and look in the direction of the image OpenGL will generate a image of all the pixels that are ``seen'' from the sonar. However, this can only provide us with optically looking images, while was not designed to does not produce camera where the sonar is and render the scene   handling computing the projection of a  and rather post-process its result with OpenCL to obtain

When our models loaded into the OpenGL scene we are ready to render.

It is also possible to compute the sonar image using the OpenGL ``blend'' feature.

@@

Modern GPUs are customized to perform computer graphics. Their theoretical peak performance is typically and order of magnitude higher than a CPU in a comparable price range. This performance can not always be achieved in practice, unless the algorithm can be adapted to use a well matured and optimized graphics processing API such as OpenGL. Our simulator uses OpenGL for most of the , then it makes little

Whether this performance can be achieved in practice 
Whenever conventional computer graphics processing can be used to 
GPUs are designed to provide the best possible graphics processing performance, and there large ecosystem of tools and libraries  available 
Using a GPU to drive a simulator is advantageous since

>>>>

\subsection{OpenGL rendering}

@@

The rendered image will appear as if we placed a window at the sonar and looked through it in the direction of the image. This window is resized to make sure that the template image perfectly fills it.

\subsection{OpenCL post-processing}

The image rendered with OpenGL is not in $(x,y)$ coordinates as we want it to be. It does, however, tell us what parts of the scene that is visible from the sonar. In addition, OpenGL can produce a depth map that reveals the distance to each template pixel. This information can be converted to a ranged sonar-like image by simply adding up all the intensity values that share the same depth for each range line. We perform this computation in OpenCL, which allow general purpose programming on GPUs and can interoperate with OpenGL quite nicely. This way we keep all the calculations on the GPU.

% It is also possible to compute the sonar image using the OpenGL ``blend'' feature.

@@

One way to automatically classify objects in SAS images is compare the imaged objects with a predefined set of templates. However, this is suboptimal as it is infeasible to create templates for all configurations of seabeds and objects. Instead we have implemented a SAS simulator that creates the templates in delayed real-time based on parameters estimated from the current scene. In our studies this improves the match between the SAS objects and the template considerably.

To obtain the delayed real-time performance we wanted to use modern GPUs. Their theoretical peak performance is typically an order of magnitude higher than a CPU in a comparable price range. While it is hard to obtain this performance in practice, we got very close by using a well matured and highly optimized graphics processing API such as OpenGL. Because of this we use OpenGL for rendering a 2D projection of a scene with 3D models of the seabed and objects. This is finally converted using the OpenCL language, which can interoperate with OpenGLTo convert this into a sonar template image we use Some additional prost-processing is required as well to form the actual template, but
